Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-08-29 draft.tex
Fearon 1994 reference added
changed statement of individual discount factors to homogenized discount factor

Future payoffs are discounted with parameters $\delta_i$, where 1/$\delta_i$ is player $i$'s discount rate for $i \in (g, s, c, p)$, $0\leq\delta_i\leq1$. Therefore payoffs for the entire game for player $i\in \{s, g, p, c\} $ can be expressed by the discounted stream of payments $\Sigma_{n=1}^{\infty} U_{in} \delta_i^{n-1}$.

@@

>>>>

Future payoffs are discounted with a common parameter $\delta$, where 1/$\delta$ is each player's discount rate and $0\leq\delta\leq1$.\footnote{All of the results that follow go through essentially unchanged in the general case where the players potentially discount at different rates. This simplifying assumption is made solely to highlight the essential mechanisms of the model.} Therefore payoffs for the entire game for player $i\in \{s, g, p, c\} $ can be expressed by the discounted stream of payments $\Sigma_{n=1}^{\infty} U_{in} \delta^{n-1}$.

@@

\item \hangindent=1cm Fearon, James D.  1994.  "Domestic Political Audiences and the Escalation of International Disputes."  \emph{The American Political Science Review} 88: 577-92.
